Estimating Planetary Habitability via Particle Swarm Optimization of CES Production Functions.

### 2018-01-16 docs/report/draft.tex
Completed few plots. Finalized code.
- Committing the results of the code here.
- Report needs the graphs and final conclusion. Maybe a few more lines
in results. Final polishing.
- Old plots removed.
- extract_sample.py is complete. Its result files added to .gitignore.
- Output format for estimations tweaked. Added iterations.

\usepackage[margin=1.2in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

@@

Tables~\ref{tab:cdhscrs} and~\ref{tab:cdhsdrs} record the CDHS values for a sample of exoplanets under CRS and DRS
respectively. Tables~\ref{tab:ceesacrs} and~\ref{tab:ceesadrs} record the same for the CEESA scores. All tables also
record the number of iterations taken to converge to a stable $\gbest$ value.

% GJ 667C e
% GJ 667C f
% GJ 832 c
% HD 40307 g
% Kapteyn’s b
% Kepler-61 b
% Kepler-62 e
% Kepler-62 f
% Kepler-174 d
% Kepler-186 f
% Kepler-283 c
% Kepler-296 f
% GJ 667C c
% GJ 163 c

\section{Results}
\begin{pointers}
\item The values and proximity to earth's habitability score.
\item Values that do not converge. Or were hard to converge.
\item Speed of convergence graphs.
\item Graph1: Iterations to convergence vs. Number of particles.
\item Graph2: Distribution of number of iterations to convergence.
\item Graph3: Iterations to convergence vs. Constraint parameters.
\end{pointers}

>>>>

\usepackage[margin=1in]{geometry}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}

@@

Tables~\ref{tab:cdhscrs} and~\ref{tab:cdhsdrs} record the CDHS values for a sample of exoplanets under CRS and DRS
respectively at $w_i=0.99$ and $w_s=0.01$. Tables~\ref{tab:ceesacrs} and~\ref{tab:ceesadrs} record the same for the
CEESA scores. All tables also record the number of iterations taken to converge to a stable $\gbest$ value.

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r r}
    \toprule
    Name & Class & $\alpha$ & $\beta$ & $Y_i$ & $i_i$ & $\gamma$ & $\delta$ & $Y_s$ & $i_s$ & $\mathit{CDHS}$\\
    \midrule
    GJ 176 b & non & 0.460 & 0.540 & 1.90 & 50 & 0.107 & 0.893 & 2.11 & 61 & 1.90\\
    GJ 667 C b & non & 0.423 & 0.577 & 1.71 & 58 & 0.692 & 0.308 & 1.81 & 54 & 1.71\\
    GJ 667 C e & psy & 0.129 & 0.871 & 1.40 & 50 & 0.258 & 0.742 & 1.39 & 55 & 1.40\\
    GJ 667 C f & psy & 0.534 & 0.466 & 1.40 & 48 & 0.865 & 0.135 & 1.39 & 47 & 1.40\\
    GJ 3634 b & non & 0.409 & 0.591 & 1.89 & 58 & 0.724 & 0.276 & 2.09 & 48 & 1.89\\
    HD 20794 c & non & 0.260 & 0.740 & 1.35 & 50 & 0.096 & 0.904 & 1.34 & 58 & 1.35\\
    HD 40307 e & non & 0.168 & 0.832 & 1.50 & 49 & 0.636 & 0.364 & 1.53 & 63 & 1.50\\
    HD 40307 f & non & 0.702 & 0.298 & 1.52 & 68 & 0.303 & 0.697 & 1.55 & 45 & 1.52\\
    HD 40307 g & psy & 0.964 & 0.036 & 1.82 & 51 & 0.083 & 0.917 & 1.98 & 55 & 1.82\\
    Kepler-186 f & hyp & 0.338 & 0.662 & 1.17 & 50 & 0.979 & 0.021 & 1.12 & 40 & 1.17\\
    Proxima Cen b & psy & 0.515 & 0.484 & 1.12 & 37 & 0.755 & 0.245 & 1.07 & 00 & 1.12\\
    TRAPPIST-1 b & non & 0.319 & 0.681 & 1.09 & 00 & 0.801 & 0.199 & 0.89 & 00 & 1.09\\
    TRAPPIST-1 c & non & 0.465 & 0.535 & 1.06 & 00 & 0.935 & 0.065 & 1.14 & 26 & 1.06\\
    TRAPPIST-1 d & mes & 0.635 & 0.365 & 0.77 & 34 & 0.475 & 0.525 & 0.73 & 47 & 0.77\\
    TRAPPIST-1 e & psy & 0.145 & 0.855 & 0.92 & 00 & 0.897 & 0.103 & 0.83 & 55 & 0.92\\
    TRAPPIST-1 g & hyp & 0.226 & 0.774 & 1.13 & 43 & 0.876 & 0.124 & 1.09 & 00 & 1.13\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CDHS under CRS by PSO.\\
    \footnotesize $\alpha$, $\beta$, $\gamma$ and $\delta$ record the parameters of Equation~\ref{eq:cdhscrs}. $Y_i$
    and $Y_s$ record the maxima for the objective functions. $i_i$ and $i_s$ specify the number of iterations taken to
    converge to a stable $\gbest$ value. Under the Class column there are four categories for the planets ---
    Psychroplanets (psy), Mesoplanets (mes), Non-Habitable planets (non) and Hypopsychroplanets (hyp).  $\mathit{CDHS}$
    is the final scores with $w_i=0.99$ and $w_s=0.01$.
  }\label{tab:cdhscrs}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r r}
    \toprule
    Name & Class & $\alpha$ & $\beta$ & $Y_i$ & $i_i$ & $\gamma$ & $\delta$ & $Y_s$ & $i_s$ & $\mathit{CDHS}$\\
    \midrule
    GJ 176 b & non & 0.395 & 0.604 & 1.90 & 059 & 0.372 & 0.627 & 2.11 & 056 & 1.90\\
    GJ 667 C b & non & 0.781 & 0.218 & 1.71 & 058 & 0.902 & 0.097 & 1.81 & 057 & 1.71\\
    GJ 667 C e & psy & 0.179 & 0.820 & 1.40 & 049 & 0.234 & 0.765 & 1.39 & 060 & 1.40\\
    GJ 667 C f & psy & 0.704 & 0.295 & 1.40 & 064 & 0.398 & 0.601 & 1.39 & 061 & 1.40\\
    GJ 3634 b & non & 0.602 & 0.397 & 1.89 & 059 & 0.429 & 0.570 & 2.09 & 077 & 1.89\\
    HD 20794 c & non & 0.014 & 0.985 & 1.35 & 050 & 0.116 & 0.883 & 1.34 & 045 & 1.35\\
    HD 40307 e & non & 0.752 & 0.247 & 1.50 & 060 & 0.677 & 0.322 & 1.53 & 050 & 1.50\\
    HD 40307 f & non & 0.887 & 0.112 & 1.52 & 051 & 0.261 & 0.738 & 1.55 & 060 & 1.52\\
    HD 40307 g & psy & 0.300 & 0.699 & 1.82 & 062 & 0.785 & 0.214 & 1.98 & 056 & 1.82\\
    Kepler-186 f & hyp & 0.073 & 0.926 & 1.17 & 046 & 0.740 & 0.259 & 1.12 & 051 & 1.17\\
    Proxima Cen b & psy & 0.045 & 0.954 & 1.12 & 057 & 0.216 & 0.783 & 1.07 & 053 & 1.12\\
    TRAPPIST-1 b & non & 0.102 & 0.897 & 1.09 & 041 & 0.000 & 0.000 & 1.00 & 065 & 1.09\\
    TRAPPIST-1 c & non & 0.471 & 0.528 & 1.06 & 044 & 0.227 & 0.772 & 1.14 & 057 & 1.06\\
    TRAPPIST-1 d & mes & 0.000 & 0.000 & 1.00 & 067 & 0.000 & 0.000 & 1.00 & 059 & 1.00\\
    TRAPPIST-1 e & psy & 0.000 & 0.000 & 1.00 & 055 & 0.000 & 0.000 & 1.00 & 057 & 1.00\\
    TRAPPIST-1 g & hyp & 0.888 & 0.111 & 1.13 & 047 & 0.949 & 0.050 & 1.09 & 046 & 1.13\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CDHS under DRS by PSO.\\
    \footnotesize Here, $\alpha$, $\beta$, $\gamma$ and $\delta$ record the parameters of Equation~\ref{eq:cdhsdrs}. The
    other columns are the same as those in Table~\ref{tab:cdhscrs}.
  }\label{tab:cdhsdrs}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r r}
    \toprule
    Name & Class & $r$ & $d$ & $t$ & $v$ & $e$ & $\rho$ & $\eta$ & $\mathit{CEESA}$ & $i$\\
    \midrule
    GJ 176 b & non & 0.304 & 0.001 & 0.375 & 0.271 & 0.050 & 0.467 & 0.808 & 1.52 &  85\\
    GJ 667 C b & non & 0.297 & 0.010 & 0.318 & 0.052 & 0.322 & 0.682 & 0.730 & 2.36 &  90\\
    GJ 667 C e & psy & 0.230 & 0.286 & 0.137 & 0.199 & 0.148 & 0.551 & 0.906 & 1.14 &  85\\
    GJ 667 C f & psy & 0.397 & 0.035 & 0.152 & 0.402 & 0.014 & 0.793 & 0.999 & 1.31 & 100\\
    GJ 3634 b & non & 0.178 & 0.175 & 0.005 & 0.194 & 0.447 & 0.894 & 0.657 & 2.07 &  94\\
    HD 20794 c & non & 0.073 & 0.142 & 0.452 & 0.190 & 0.144 & 0.953 & 0.635 & 1.20 &  78\\
    HD 40307 e & non & 0.156 & 0.307 & 0.185 & 0.033 & 0.319 & 0.428 & 0.939 & 2.69 &  88\\
    HD 40307 f & non & 0.272 & 0.231 & 0.064 & 0.305 & 0.127 & 0.676 & 0.802 & 1.28 &  77\\
    HD 40307 g & psy & 0.113 & 0.219 & 0.066 & 0.454 & 0.148 & 0.711 & 0.991 & 3.26 &  92\\
    Kepler-186 f & hyp & 0.039 & 0.159 & 0.116 & 0.329 & 0.357 & 0.253 & 0.919 & 1.35 &  70\\
    Proxima Cen b & psy & 0.272 & 0.173 & 0.284 & 0.193 & 0.079 & 0.615 & 0.114 & 0.99 &  75\\
    TRAPPIST-1 b & non & 0.488 & 0.151 & 0.039 & 0.193 & 0.129 & 0.151 & 0.014 & 0.99 &  87\\
    TRAPPIST-1 c & non & 0.172 & 0.236 & 0.275 & 0.242 & 0.075 & 0.969 & 0.962 & 1.06 &  80\\
    TRAPPIST-1 d & mes & 0.106 & 0.308 & 0.075 & 0.218 & 0.293 & 0.844 & 0.017 & 0.99 &  93\\
    TRAPPIST-1 e & psy & 0.189 & 0.266 & 0.192 & 0.094 & 0.260 & 0.371 & 0.006 & 0.99 &  84\\
    TRAPPIST-1 g & hyp & 0.326 & 0.186 & 0.143 & 0.278 & 0.067 & 0.315 & 0.021 & 1.00 &  76\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CEESA under DRS by PSO.\\
    \footnotesize $r$, $d$, $t$, $v$, $e$, $\rho$ and $eta$ record the parameters of Equation~\ref{eq:ceesadrs}.
    $\mathit{CEESA}$ records the maxima of the objective function. $i$ specifies the number of iterations taken to
    converge to the maxima.
  }\label{tab:ceesadrs}
\end{table}

\begin{table}
  \centering
  \begin{tabular}{l r r r r r r r r r}
    \toprule
    Name & Class & $r$ & $d$ & $t$ & $v$ & $e$ & $\rho$ & $\mathit{CEESA}$ & $i$\\
    \midrule
    GJ 176 b & non & 0.194 & 0.020 & 0.315 & 0.465 & 0.006 & 0.398 & 1.88 &  86\\
    GJ 667 C b & non & 0.162 & 0.289 & 0.090 & 0.087 & 0.372 & 0.836 & 3.54 & 107\\
    GJ 667 C e & psy & 0.373 & 0.032 & 0.134 & 0.304 & 0.157 & 0.217 & 1.25 &  71\\
    GJ 667 C f & psy & 0.394 & 0.006 & 0.043 & 0.360 & 0.196 & 0.490 & 1.44 &  81\\
    GJ 3634 b & non & 0.351 & 0.122 & 0.006 & 0.069 & 0.453 & 0.439 & 2.89 &  96\\
    HD 20794 c & non & 0.101 & 0.077 & 0.691 & 0.071 & 0.059 & 0.756 & 1.58 &  94\\
    HD 40307 e & non & 0.069 & 0.091 & 0.097 & 0.173 & 0.569 & 0.768 & 5.29 &  94\\
    HD 40307 f & non & 0.285 & 0.161 & 0.053 & 0.443 & 0.058 & 0.342 & 1.42 &  73\\
    HD 40307 g & psy & 0.156 & 0.010 & 0.081 & 0.302 & 0.451 & 0.612 & 7.15 &  94\\
    Kepler-186 f & hyp & 0.036 & 0.017 & 0.082 & 0.383 & 0.483 & 0.929 & 1.68 &  85\\
    Proxima Cen b & psy & 0.352 & 0.383 & 0.103 & 0.059 & 0.103 & 0.936 & 0.89 &  83\\
    TRAPPIST-1 b & non & 0.148 & 0.147 & 0.344 & 0.269 & 0.093 & 0.767 & 0.94 &  81\\
    TRAPPIST-1 c & non & 0.038 & 0.060 & 0.575 & 0.321 & 0.005 & 0.602 & 1.17 &  86\\
    TRAPPIST-1 d & mes & 0.023 & 0.065 & 0.475 & 0.391 & 0.045 & 0.830 & 0.84 &  79\\
    TRAPPIST-1 e & psy & 0.176 & 0.464 & 0.253 & 0.103 & 0.004 & 0.920 & 0.86 &  81\\
    TRAPPIST-1 g & hyp & 0.060 & 0.086 & 0.310 & 0.540 & 0.004 & 0.848 & 0.97 &  86\\
    \bottomrule
  \end{tabular}
  \caption{Estimated values of CEESA under CRS by PSO.\\
    \footnotesize Here, $r$, $d$, $t$, $v$, $e$ and $\rho$ record the parameters of Equation~\ref{eq:ceesacrs}. Since
    under the CRS constraint $\eta=1$, there is no need for the parameter in the problem.
  }\label{tab:ceesacrs}
\end{table}

% \begin{pointers}
% \item The values and proximity to earth's habitability score.
% \item Values that do not converge. Or were hard to converge.
% \item Speed of convergence graphs.
% \item Graph1: Iterations to convergence vs. Number of particles.
% \item Graph2: Distribution of number of iterations to convergence.
% \item Graph3: Iterations to convergence vs. Constraint parameters.
% \end{pointers}
